A Formal Model of Checked C

### 2022-08-10 sandp23/introduction.tex
Adding intro

\myparagraph{Type-Directed Program Partitioning}
Our first contribution is a clear program partition between checked and unchecked code regions
and ensures that a \systemname program execution \textit{cannot crash} due to spatial safety violations.
We restrict the checked and unchecked pointers usage only in checked and unchecked code regions, respectively;
and develop tainted pointers for the communication between the two regions.
Heap is partitioned into two parts: a \textit{checked heap} containing all checked pointers
 and an \textit{unchecked heap} that is sandboxed.
Tainted pointers exist in the unchecked heap region and must be verified each time being used.

\myparagraph{Formalizing the Type System, Semantics and Compiler}
%
Our second contribution is a core formalism named \lang, which extends
\citet{li22checkedc} with the non-crashing guarantee and other new features below.
We prove formally the \textit{non-crashing theorem}, i.e., 
a well-typed \lang program can never crash due to spatial safety violations.
We maintain the compiler formalism with the new features extended in \systemname.
Especially, we maintain the bound-check insertions for array accesses 
without ``fat'' pointer compilation scheme, while keeping the non-crashing guarantee.
To certify the simulation relation between the \lang semantics and the compiler,
we utilize the model-based randomized testing.
This is done by a conversion tool that converts expressions from \lang into
actual \checkedc code that can be compiled by the Clang \checkedc
compiler. We create a program random generator 
based on the
typing rules of \lang and ensure that \lang and Clang Checked C are consistent after conversion, both statically and
dynamically.  
To the best of our knowledge, 
\lang is the first C(-like) language and compiler formalism with the program partitioning mechanism.

>>>>

\myparagraph{Type-Directed Program Partitioning}
We present a type-directed program partition technique to separate checked and unchecked code regions and ensure that the code in checked region~\textit{cannot crash} due to spatial safety violations.
Our type system restricts checked and tainted (or unchecked) pointers usage only in~\cregion and~\ucregion, respectively.
Our modular design enables us to use existing sandboxed techniques to enforce memory and execution isolation.

\myparagraph{Formalizing the Type System, Semantics and Compiler}
%
We developed a core formalism named~\lang, which extends
\citet{li22checkedc}~\checkedc formalism with the non-crashing guarantee and other new features below.
We prove formally the~\emph{non-crashing theorem}, i.e., 
a well-typed~\lang program can never crash due to spatial safety violations.
We utilize the model-based randomized testing (CITE) to certify the simulation relation between the~\lang semantics and the compiler.
Specifically, we use a conversion tool that converts expressions from~\lang into actual~\checkedc code that can be compiled by the \checkedc compiler. We create a random program generator 
based on the typing rules of~\lang and ensure that~\lang and~\checkedc compiler are consistent after conversion, both statically and dynamically.  
To the best of our knowledge,~\lang is the first C(-like) language and compiler formalism with the program partitioning mechanism.
